\documentclass{article}[a4paper]
\

\begin{document}
## PROJECT UTKARSH
### STATEMENT OF PURPOSE

Name: Aum Kulkarni  
Class: D6AD    
Roll No: 36     
Email: 2021.aum.kulkarni@ves.ac.in     
\begin{enumerate}
    \item 1. Elaborate on your knowledge of web development    
    I have foundational knowledge about front end development with HTML and CSS. Also I used React JS for making websites, including  hackathons.
    On the back-end, I have a basic knowledge of how web servers work which has helped in my backend development projects which were made using technologies like Django and Express.
    I also have some experience with version control such as Git and GitHub and regularly keep my projects updated on the same.
    2. How comfortable are you with Python?    
    I have worked in Python throughout the second year as it was a part of our curriculum. I had also participated in AIColegions HackAIthon as well as completed a course related to image processing of space images. This has helped me have a grasp on doing things in Python and has also helped me in making use of the various packages used in image processing and data science.
    3. Are you committed to working with this project until its completion.    
    Yes, I am committed to working through the project to completion. I understand the value of the project to both me and the company that I will make contributions for. Keeping this in mind I aim to dedicate time to work on the project to its completion.
    4. Tell us about your technical skills in general    
    I have worked on various projects involving various languages from lower level languages such as C to higher level languages like Python including Java, C++ and Javascript.
    Having knowledge of lower level programming constructs has given me an understanding of how other libraries and frameworks work, which are built using them. 
    This has helped in efficient debugging of code and having a sense of how things work with each other thus making better decisions overall.
    
    5. What are your biggest strengths?    
        - Discipline - I can put distractions aside and focus on my work. My discipline has helped me perform well in my academics and meet the deadlines for academic work.
        - Ability to learn new things quickly - I can pick up new things fairly quickly due to my exposure to a wide range of technologies. This enables me to grasp new concepts and apply them in practical situations.
    6. What are your biggest weaknesses?    
        - I can get too invested in completing a particular task, which sometimes negatively impacts my performance.
        - Efficiency - I sometimes become less efficient in search for a better alternatives and researching things which impacts me to get things done as efficiently as possible
\end{enumerate}
\end{document}
